Counting And Confusion: Bayesian Rate Estimation With Multiple Populations

### 2013-02-20 many.tex
Added Tom Dent to acknowledgements.

\begin{acknowledgments}
  We thank Kipp Cannon, Chad Hanna, Drew Keppel, Richard
  O'Shaughnessy, and Ted von Hippel for discussions and suggestions
  about this manuscript.  IM and WMF acknowledge the hospitality of
  KITP, supported in part by the National Science Foundation under NSF
  Grant PHY11-25915.  CC's work was carried out at the Jet Propulsion
  Laboratory, California Institute of Technology, under contract to
  the National Aeronautics and Space Administration.  CC also
  gratefully acknowledges support from NSF grant PHY1068881.  JG's
  work is supported by the Royal Society.  Copyright 2013.  All rights
  reserved.
\end{acknowledgments}

>>>>

\begin{acknowledgments}
  We thank Kipp Cannon, Thomas Dent, Chad Hanna, Drew Keppel, Richard
  O'Shaughnessy, and Ted von Hippel for discussions and suggestions
  about this manuscript.  IM and WMF acknowledge the hospitality of
  KITP, supported in part by the National Science Foundation under NSF
  Grant PHY11-25915.  CC's work was carried out at the Jet Propulsion
  Laboratory, California Institute of Technology, under contract to
  the National Aeronautics and Space Administration.  CC also
  gratefully acknowledges support from NSF grant PHY1068881.  JG's
  work is supported by the Royal Society.  Copyright 2013.  All rights
  reserved.
\end{acknowledgments}
